\vspace{-2.5em} Spatio-angular transfer functions for fluorescence microscopes\vspace{-1em}

### 2018-04-17 notes/2018-02-23-spatio-angular-kernel/report/report.tex
Numerics and analytics match. Paraxial spatio-angular otf done.

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%

\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

The spatio-angular PSF under the paraxial approximation is given by
\begin{align}
      h^{(p)}(\rd{}', \so{}) \propto \left({a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{a^{(p)}}^2(r_d') + {4b^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
\end{align}
We rewrite the PSF in the following form to make plotting and interpretation easier
\begin{align}
  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_0^2}^{(p)}(\rd{}')y_0^2(\so{}),\\
  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
  {h_0^2}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right].
\end{align}

@@

In Appendix \ref{paraxialotf} we calculate the paraxial OTF for a single-view
fluorescence microscope as
\begin{align}
  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m),\label{eq:fullotf}\\
  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + \text{NA}^2/(2n_o^2)},\\
  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + \text{NA}^2/(2n_o^2)]}.
\end{align}
where
\begin{align}
  {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  {B}^{(p)}(\nu) &= \frac{\text{NA}^2}{2\pi n_o^2}\left[\left(1 - \frac{\nu^2}{\nu_o^2}\right)\arccos\left(\frac{\nu}{2\nu_o}\right) + \left(1 + \frac{\nu^2}{2\nu_o^2}\right)\frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
\end{align}

Notice that the paraxial OTF is rotationally symmetric, so we can write in terms
of $\nu$ instead of the complete spatial frequency vector $\bs{\nu}$. This will
no longer be true when we leave the paraxial approximation or add polarizing
filters to the system. Also, notice that ${A}^{(p)}(\nu)$ is the spatial OTF for
an incoherent imaging system under the paraxial and scalar approximations
\cite{goodman1996}.

If our sample consists of isotropic distributions of fluorophores only, then we
can ignore the ${H_2^0}^{(p)}(\nu)$ term in the OTF. As the NA approaches zero,
${B}^{(p)}(\nu)$ disappears and we recover the spatial OTF from the
spatio-angular OTF as expected. For non-zero NA the difference between the OTF
with and without the scalar approximation is $2{B}^{(p)}(\nu)$. We can interpret
this difference as an electromagnetic correction to the scalar OTF. The
correction is proportional to $\frac{\text{NA}^2}{n_o^2}$, so it is a small term
for all but high NA objectives.

@@

We can use the spatio-angular OTF to derive the spatial OTF for any distribution
of fluorophores. As an example, let's derive the spatial OTF for a $z$-oriented
fluorophore. The object is $f(\ro{}, \so{}) = \delta(\ro{})\delta(\so{} - \mh{z})$. We can calculate
the angular spectrum of the object as
$F_l^m(\bs{\nu}) = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \delta(\so{} - \mh{z})y_l^m(\so{})\me{}^{-i2\pi M\ro{}\cdot\bs{\nu}} =
y_l^m(\mh{z})$. Finally, we can plug in the angular spectrum
into equation \ref{eq:freqforwardint}
\begin{align}
  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) y_l^m(\mh{z}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}, \label{eq:freqforwardint}
\end{align}
then plug in the spatio-angular OTF from Eq. \ref{eq:fullotf} and evaluate the
sum to find
\begin{align}
  g(\rd{}) \propto \int_{\mathbb{R}^2}d\nu{}\, \left[H_0^0(\nu)y_0^0(\mh{z}) + H_2^0(\bs{\nu})y_2^0(\mh{z})\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
\end{align}
So the spatial OTF for a $z$ oriented dipole is given by
\begin{align}
  H_{\mh{z}}(\nu) \propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu).
\end{align}
The main result is that the spatial OTF for any dipole distribution is a linear
combination of the OTFs for the spherical harmonics. I am partially hesitant to
refer to $H_{\mh{z}}(\nu)$ as an OTF because it is object dependent, but the
vocabulary is fine if it is understood that the sample only contains
$z$-oriented dipoles. For general distributions, the complete spatio-angular OTF
should be used instead of deriving the transfer function for every individual
fluorophore.

Fig. \ref{fig:para} shows the spatio-angular OTF for a microscope with
$\text{NA}=0.8$ and $n=1.33$. The most important feature of this figure is that
${H_0^0}^{(p)}(\nu)$ is a low-pass filter compared to ${H_0^2}^{(p)}(\nu)$ with
a maximum difference of $\sim 7\%$ (with larger difference for higher NA). If the difference between
${H_0^0}^{(p)}(\nu)$ and ${H_0^2}^{(p)}(\nu)$ is not completely obscured by
noise, we will be able to exploit the difference to estimate the out-of-plane
angle of dipoles with a single image (putting aside the ill-posedness of the
problem).

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/psfs.pdf}
   \caption{\textbf{Left:} Paraxial spatio-angular point spread function for a
     single-view fluorescence microscope with NA=0.8 and $n_o$=1.33. The solid
     line is the PSF for $y_0^0$ distributions and the dashed line is the PSF
     for $y_2^0$ distributions. The dotted line is the $y_2^0$ PSF normalized
     for comparison with the $y_0^0$ PSF. The $y_2^0$ distributions includes
     ``negative'' fluorophores, so it gives rise to a negative PSF.
     \textbf{Right:} Numerical paraxial spatio-angular optical transfer function
     for the same microscope. The $y_0^0$ term has a comparatively low-pass
     response while the $y_2^0$ term has a comparatively high-pass response.}
   \label{fig:para}
\end{figure}

@@

\section{Paraxial optical transfer function}\label{paraxialotf}
In this appendix we calculate the paraxial OTF for a single-view fluorescence
microscope. We start with Eq. \ref{eq:otfdef2}
\begin{align}
  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.\label{eq:otfdef2}
\end{align}
We could plug in the paraxial PSF and evaluate the integrals, but this will lead
us to Fourier transforms that cannot be found in tables. Instead we use a trick
from scalar Fourier optics and write the OTF in terms of the detected electric
field \cite{goodman1996}
\begin{align}
  H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \left|\mb{e}_d(\rd{}', \so{})\right|^2 y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
\end{align}
Next, we manipulate this equation to
\begin{align}
  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}', \so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}},\\
  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\delta(\rd{}'' - \rd{}')\, \me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\tau}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
  H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
\end{align}
We have followed the proof for the Wiener-Kinchin theorem \cite{papoulis2002, wiener} to explicitly show how the angular integral affects the usual scalar
calculation. Eq. \ref{eq:hlmauto} shows that we can calculate the OTF by taking
the vector autocorrelation of the spatial CTF then projecting the result onto
the spherical harmonics.

We will rewrite Eq. \ref{eq:hlmauto} in two parts

>>>>

%%%%%%%%%%%%
% Packages %
%%%%%%%%%%%%
\usepackage[dvipsnames]{xcolor}
\hyphenpenalty=10000
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

The spatio-angular PSF under the paraxial approximation is given by
\begin{align}
      h^{(p)}(\rd{}', \so{}) \propto \left({a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d')\right)y_0^0(\so{}) + \frac{1}{\sqrt{5}}\left(-{a^{(p)}}^2(r_d') + {4b^{(p)}}^2(r_d')\right)y_2^{0}(\so{})\label{eq:para}.
\end{align}
We rewrite the PSF in the following form to make plotting and interpretation easier
\begin{align}
  h^{(p)}(\rd{}', \so{}) &= {h_0^0}^{(p)}(\rd{}')y_0^0(\so{}) + {h_2^0}^{(p)}(\rd{}')y_2^0(\so{}),\\
  {h_0^0}^{(p)}(\rd{}') &\equiv {a^{(p)}}^2(r_d') + 2{b^{(p)}}^2(r_d'),\\
  {h_2^0}^{(p)}(\rd{}') &\equiv \frac{1}{\sqrt{5}}\left[- {a^{(p)}}^2(r_d') + 4{b^{(p)}}^2(r_d')\right]. \label{eq:concisepsf}
\end{align}

@@

In Appendix \ref{paraxialotf2} we calculate the paraxial OTF for a single-view
fluorescence microscope as
\begin{align}
  {H_l^m}^{(p)}(\nu) &= {H_0^0}^{(p)}(\nu)\delta(l, m) + {H_2^0}^{(p)}(\nu)\delta(l-2, m), \label{eq:fullotf} \\
  {H_0^0}^{(p)}(\nu) &\equiv \frac{A^{(p)}(\nu) + 2B^{(p)}(\nu)}{1 + (\text{NA}/n_o)^2},\\
  {H_2^0}^{(p)}(\nu) &\equiv \frac{-A^{(p)}(\nu) + 4B^{(p)}}{\sqrt{5}\, [1 + (\text{NA}/n_o)^2]},
\end{align}
where
\begin{align}
  {A}^{(p)}(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  B^{(p)}(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).                 
\end{align}

Notice that the paraxial OTF is rotationally symmetric, so we can write in terms
of $\nu$ instead of the complete spatial frequency vector $\bs{\nu}$. This will
not be true when we leave the paraxial approximation or add polarizing filters
to the system. Also, notice that ${A}^{(p)}(\nu)$ is the spatial OTF for an
incoherent imaging system (the Fourier transform of an Airy pattern) under the
paraxial and scalar approximations \cite{goodman1996}.

If our sample consists of isotropic distributions of fluorophores only, then we
can ignore the ${H_2^0}^{(p)}(\nu)$ term in the OTF. As the NA approaches zero,
${B}^{(p)}(\nu)$ disappears and we recover the scalar OTF from the vector
spatio-angular OTF as expected. For non-zero NA the difference between the OTF
with and without the scalar approximation is $2{B}^{(p)}(\nu)$. We can interpret
this difference as an electromagnetic correction to the scalar OTF. The
correction is proportional to $\left(\text{NA}/{n_o}\right)^2$, so it is a small term
for all but high NA objectives.

@@

We can use the spatio-angular OTF to derive the spatial OTF for any distribution
of fluorophores. As an example, let's derive the spatial OTF for a $z$-oriented
fluorophore. The object is $f(\ro{}, \so{}) = \delta(\ro{})\delta(\so{} - \mh{z})$. We can calculate
the angular spectrum of the object as
$F_l^m(\bs{\nu}) = \int_{\mathbb{R}^2}d\ro{}\int_{\mathbb{S}^2}d\so{} \delta(\so{} - \mh{z})y_l^m(\so{})\me{}^{-i2\pi M\ro{}\cdot\bs{\nu}} =
y_l^m(\mh{z})$. Finally, we can plug in the angular spectrum
into equation \ref{eq:freqforwardint}
\begin{align}
  g(\rd{}) = \sum_{l=0}^{\infty} \sum_{m=-l}^l \int_{\mathbb{R}^2}d\bs{\nu}{}\, H_l^m(\bs{\nu}) y_l^m(\mh{z}) \me^{i 2\pi \rd{}\cdot\bs{\nu}}, \label{eq:freqforwardint}
\end{align}
then plug in the spatio-angular OTF from Eq. \ref{eq:fullotf} and evaluate the
sum to find
\begin{align}
  g(\rd{}) \propto \int_{\mathbb{R}^2}d\nu{}\, \left[H_0^0(\nu)y_0^0(\mh{z}) + H_2^0(\bs{\nu})y_2^0(\mh{z})\right] \me^{i 2\pi \rd{}\cdot\bs{\nu}}. \label{eq:freqforwardint}
\end{align}
So the spatial OTF for a $z$ oriented dipole is given by
\begin{align}
  H_z^{(p)}(\nu) &\propto \sqrt{\frac{1}{4\pi}}H_0^0(\nu) + \sqrt{\frac{5}{4\pi}}H_2^0(\nu), \\
    H_z^{(p)}(\nu) &= \frac{1}{2}\left(\frac{n_o}{\text{NA}}\right) B^{(p)}(\nu).
\end{align}
The most important result is that the spatial OTF for \textbf{any} dipole
distribution is a linear combination of just two OTFs---one for each spherical
harmonic. The same is true for the PSFs---the PSF for any dipole
distribution is a linear combination of just two PSFs.

Fig. \ref{fig:para} shows four important paraxial PSFs and OTFs for a microscope
with $\text{NA}=0.8$ and $n=1.33$. Notice that the OTF for $z$-oriented
dipoles is negative at high frequencies. An OTF that crosses zero will give a
contrast inversion in a Siemens star test target. The negative OTF is a direct
consequence of the donut-shaped point spread function. If we arranged a pattern
of $z$-oriented dipoles with a sinusoid spatial frequency near the cutoff
frequency, the regions of low intensity would report the positions of the
fluorophores.

\begin{figure}[h]
 \captionsetup{width=1.0\linewidth}
 \centering
   \centering
   \includegraphics[width = 1.\textwidth]{../calculations/compare-ft/psfs.pdf}
   \caption{\textbf{Left:} Point spread functions and \textbf{Right:} optical
     transfer functions for a single-view fluorescence microscope with
     $\text{NA}=0.8$ and $n_o=1.33$ under the paraxial approximation.
     \textbf{Black:} $l=0, m=0$ spherical harmonic---an isotropic distribution
     of fluorophores. \textcolor{blue}{\textbf{Blue:}} $l=2, m=0$ spherical
     harmonic---negative fluorophores near the transverse plane, positive
     fluorophores near the optical axis. \textcolor{red}{\textbf{Red:}}
     $x$-oriented dipole. \textcolor{OliveGreen}{\textbf{Green:}} $y$-oriented
     dipole.}
   \label{fig:para}
\end{figure}

@@

% \section{Paraxial optical transfer function}\label{paraxialotf}
% In this appendix we calculate the paraxial OTF for a single-view fluorescence
% microscope. We start with Eq. \ref{eq:otfdef2}
% \begin{align}
%   H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, h(\rd{}', \so{}) y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
% \end{align}
% We could plug in the paraxial PSF and evaluate the integrals, but this will lead
% us to Fourier transforms that cannot be found in tables. Instead we use a trick
% from scalar Fourier optics and write the OTF in terms of the detected electric
% field \cite{goodman1996}
% \begin{align}
%   H_l^m(\bs{\nu}) \propto \int_{\mathbb{S}^2}d\so{}\int_{\mathbb{R}^2}d\rd{}'\, \left|\mb{e}_d(\rd{}', \so{})\right|^2 y_l^m(\so{})\thinspace\me^{-i 2\pi \rd{}'\cdot\bs{\nu}}.
% \end{align}
% Next, we manipulate this equation to
% \begin{align}
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}', \so{})\, \me^{-i 2\pi \rd{}'\cdot\bs{\nu}},\\
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\delta(\rd{}'' - \rd{}')\, \me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\int_{\mathbb{R}^2}d\rd{}'\, \int_{\mathbb{R}^2}d\rd{}''\, \mb{e}^{\dagger}_d(\rd{}', \so{})\mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi\bs{\tau}(\rd{}'' - \rd{}')}\me^{-i 2\pi \rd{}''\cdot\bs{\nu}},\\
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\left[\int_{\mathbb{R}^2}d\rd{}'\, \mb{e}^{\dagger}_d(\rd{}', \so{}) \me^{i 2\pi\rd{}'\cdot \bs{\tau}}\right]\left[\int_{\mathbb{R}^2}d\rd{}''\, \mb{e}_d(\rd{}'', \so{})\me^{-i 2\pi \rd{}''\cdot(\bs{\nu} + \bs{\tau})}\right],\\
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{})\int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}; \so{})\mb{E}(\bs{\tau} + \bs{\nu}; \so{}). \label{eq:hlmauto}
% \end{align}
% We have followed the proof for the Wiener-Kinchin theorem \cite{papoulis2002, wiener} to explicitly show how the angular integral affects the usual scalar
% calculation. Eq. \ref{eq:hlmauto} shows that we can calculate the OTF by taking
% the vector autocorrelation of the spatial CTF then projecting the result onto
% the spherical harmonics.

% We will rewrite Eq. \ref{eq:hlmauto} in two parts
% \begin{align}
%   H_l^m(\bs{\nu}) &\propto \int_{\mathbb{S}^2}d\so{}\, y_l^m(\so{}) H(\bs{\nu}; \so{})  \label{eq:hlmauto2}\\
%   H(\bs{\nu}; \so{}) &\equiv \int_{\mathbb{R}^2}d\bs{\tau}\,\mb{E}^{\dagger}(\bs{\tau}- \bs{\nu}/2; \so{})\mb{E}(\bs{\tau} + \bs{\nu}/2; \so{}). \label{eq:hlmspatial}
% \end{align}
% Notice the change of variable to simplify the autocorrelation. In the previous
% section we calculated the CTF in the paraxial case as 
% \begin{align}
%   {\mb{E}}^{(p)}(\bs{\nu}; \so{}) =
% \begin{bmatrix}
%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\cos\phi_\nu y_1^0(\so{})\\
%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}\nu\sin\phi_\nu y_1^0(\so{})\\
%   0\\
%   \end{bmatrix}\, \Pi\left(\frac{\nu}{\nu_o}\right). \label{eq:ctfparax}
% \end{align}
% By introducing $\bs{\tau} \equiv \tau_x\mh{x} + \tau_y\mh{y} \equiv \tau\cos\phi_\tau\mh{x} + \tau\sin\phi_\tau\mh{y}$
% we can plug Eq. \ref{eq:ctfparax} into Eq. \ref{eq:hlmspatial} and find that
% \begin{align}
%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &\begin{bmatrix}
%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x - \frac{1}{2}\nu_x) y_1^0(\so{})\\
%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y - \frac{1}{2}\nu_y) y_1^0(\so{})\\
%   0\\
% \end{bmatrix}^{\dagger}
%   \begin{bmatrix}
%   y_1^1(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_x + \frac{1}{2}\nu_x) y_1^0(\so{})\\
%   y_1^{-1}(\so{}) + \frac{2}{\nu_o}\frac{\text{NA}}{n_o}(\tau_y + \frac{1}{2}\nu_y) y_1^0(\so{})\\
%   0\\
% \end{bmatrix}\nonumber \\
%   &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
% \end{align}
% Expanding the inner product gives
% \begin{align}
%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
%       \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
%                                                                  &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
%                                                                  &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x - \frac{1}{2}\nu_x) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^1(\so{})\right\}(\tau_x + \frac{1}{2}\nu_x) \nonumber \\
%   &\left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y - \frac{1}{2}\nu_y) + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})y_1^{-1}(\so{})\right\}(\tau_y + \frac{1}{2}\nu_y) \nonumber \\  
% &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
% \end{align}
% All of the terms with a single $(\tau_\cdot \pm \frac{1}{2}\nu_\cdot)$ term are
% correlations of an odd function with an even function, so they are zero.
% Therefore
% \begin{align}
%     H^{(p)}(\bs{\nu}; \so{}) \propto \int_{\mathbb{R}^2}d\bs{\tau}\, &
%       \{y_1^1(\so{})\}^2  + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_x - \frac{1}{2}\nu_x)(\tau_x + \frac{1}{2}\nu_x) + \nonumber \\
%                                                                  &\{y_1^{-1}(\so{})\}^2 + \left\{\frac{2}{\nu_o}\frac{\text{NA}}{n_o}y_1^0(\so{})\right\}^2(\tau_y - \frac{1}{2}\nu_y)(\tau_y + \frac{1}{2}\nu_y) + \nonumber \\
% &\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right). 
% \end{align}
% After expanding the spherical harmonics we can rewrite this equation in terms of
% two autocorrelations
% \begin{align}
%     H^{(p)}(\nu; \so{}) &\propto \Big[A^{(p)}(\nu) + 2B^{(p)}(\nu)\Big]y_0^0(\so{}) + \frac{1}{\sqrt{5}}\Big[-A^{(p)}(\nu) + 4B^{(p)}(\nu)\Big]y_2^0(\so{})\label{eq:hinter}
% \end{align}
% where
% \begin{align}
%   A^{(p)}(\nu) &\equiv \frac{1}{\pi\nu_o^2}\int_{\mathbb{R}^2}d\bs{\tau}\, \Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right),\\
%   B^{(p)}(\nu) &\equiv \frac{\text{NA}^2}{\pi\nu_o^4n_o^2} \int_{\mathbb{R}^2}d\bs{\tau}\, \left[(\tau_x - \nu_x/2)(\tau_x + \nu_x/2) + (\tau_y - \nu_y/2)(\tau_y + \nu_y/2)\right]\nonumber \\ &\hspace{17em}\Pi\left(\frac{\tau - \nu/2}{\nu_o}\right)\Pi\left(\frac{\tau + \nu/2}{\nu_o}\right).
% \end{align}
% I've used the constant $\frac{1}{\pi\nu_o^2}$ in front of both autocorrelations
% so that the results are normalized, but these constants are not essential. Also,
% notice that both autocorrelations are rotationally symmetric, so we can write
% them as a function of $\nu$ instead of $\bs{\nu}$. We can evaluate these
% integrals with the help of the geometric construction shown in Figure
% \ref{fig:geometry} \cite{goodman1996}.

% \begin{figure}[h]
%  \captionsetup{width=1.0\linewidth}
%  \centering
%    \centering
%    \includegraphics[width = 0.8\textwidth]{../figures/geometry/geometry.pdf}
%    \caption{Geometric construction for evaluating $A^{(p)}(\bs{\nu})$ and
%      $B^{(p)}(\bs{\nu})$. We need to find the boundaries of integration for the
%      overlapping region of two circles with radius $\nu_o$ and distance $\nu$
%      between their centers. The region is given by four times the difference in
%      area between a sector of angle $\arccos\left(\frac{\nu}{2\nu_o}\right)$ and
%      a triangle with base $\nu/2$ and hypotenuse $\nu_o$.}
%    \label{fig:geometry}
% \end{figure}
